A_pilot_1

### 2018-08-29 experiments/A_pilot_1/writeup/A_pilot_1.Rmd
renaming to A_pilot_1
tidying A

---
title: "Experiment 0 pilot"
author: "Matt Green"
output:
  html_document:
    toc: yes
    toc_float: true
    mathjax: default
    template: default
    code_folding: show
    theme: default

---

@@

```{r load knitr}
library(knitr)
```

@@

```{r load libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(broom)
library(dotwhisker)
library(grid)
library(gridExtra)
library(lme4)
# R CMD INSTALL broom.mixed # https://github.com/bbolker/broom.mixed
```

@@

```{r "make the data.txt file unless it's already there; read the data from file, add some vars and code the added vars"}

@@

```{r}
d <- subset(d, err==0)
```

@@

### Uncapped

```{r fig.show='hide', warning=FALSE, echo=FALSE}
# all the (correct) RTs
summary(d$rt_ms)

@@

myg1 <- grid.arrange(ga1untrimmed, ga2untrimmed, nrow=2, top = textGrob("Untrimmed",gp=gpar(fontsize=20,font=3)))
```

### Capped at 0 ms and 10,000 ms

```{r fig.show='hide', warning=FALSE, echo=FALSE}
# now with a simple cap imposed to select RTs between 0 and 10000 ms
summary(d$rt_ms[d$rt_ms >= 0 & d$rt_ms<10000])

@@

myg2 <- grid.arrange(ga1trimmed, ga2trimmed, nrow=2, top = textGrob("Trimmed at 10,1000 ms",gp=gpar(fontsize=20,font=3)))
```

```{r, fig.width=10,fig.height=10}
grid.arrange(myg1, myg2, nrow=2)
```

@@

```{r}
dat %>% 
  gather(key=rt_metric, value=rt_value, rt_ms, rt_log, rt_reciprocal) %>%
  filter(rt_metric=="rt_log") %>%
  ggplot(aes(group=vag, y=rt_value)) +
  geom_boxplot(aes(x=item, col=vag))
```

@@

```{r, lmer1}
lmer1.ms  <- lmer(data=dat, rt_ms ~         vag + subit + quan + gap + side + (1|subject) + (1|item))
lmer1.log <- lmer(data=dat, rt_log ~        vag + subit + quan + gap + side + (1|subject) + (1|item))
lmer1.rcp <- lmer(data=dat, rt_reciprocal ~ vag + subit + quan + gap + side + (1|subject) + (1|item))

@@

dwplot(models, vline = geom_vline(xintercept = 0)) + facet_wrap(~model, scales="free", ncol=1)

```

```{r mler on logrt}
lmer2.log <- lmer(data=dat, rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item))
dwplot(lmer2.log %>% tidy() %>% filter(group=="fixed")) + 
  ggtitle("rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item)")

lmer2 <- lmer(data=dat, rt_reciprocal~subit*vag + (vag|subject) + (vag|item))
# lmer3 is closer to the original anova than lmer2
lmer3 <- tidy(lme4::lmer(data=dat, rt_reciprocal~vag*subit+quan+gap + (vag+subit|subject) + (vag|item)))
dwplot(lmer3 %>% filter(group=="fixed"), vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2)) + xlab("Coefficient")
```

>>>>

---
title: "A_pilot_1"
author: "Matt Green"
output:
  html_document:
    toc: yes
---

@@

@@

```{r load libraries, message=FALSE, warning=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(dotwhisker)
library(grid)
library(gridExtra)
library(lme4)
# R CMD INSTALL broom.mixed # https://github.com/bbolker/broom.mixed
```

@@

```{r "make the data.txt file unless it's already there; read the data from file, add some vars and code the added vars", message=FALSE}

@@

```{r, "remove error trials"}
d <- subset(d, err==0)
```

@@

### Untrimmed

Notice min is -6; max in 20258.

```{r, "make untrimmed plot", fig.show='hide', warning=FALSE, echo=FALSE}
# all the (correct) RTs
summary(d$rt_ms)

@@

myg1 <- grid.arrange(ga1untrimmed, ga2untrimmed, nrow=2, top = textGrob("Untrimmed", gp = gpar(fontsize=20, font=3)))
```

### Trimmed at 0 ms and 10,000 ms

```{r, "make trimmed plot", fig.show='hide', warning=FALSE, echo=FALSE}
# now with a simple cap imposed to select RTs between 0 and 10000 ms
summary(d$rt_ms[d$rt_ms >= 0 & d$rt_ms<10000])

@@

myg2 <- grid.arrange(ga1trimmed, ga2trimmed, nrow=2, top = textGrob("Trimmed at 0 and 10,1000 ms", gp = gpar(fontsize=20, font=3)))
```

```{r, "put trimmed-untrimmed plot", fig.width=10,fig.height=10, echo=FALSE}
grid.arrange(myg1, myg2, nrow=2)
```

@@

```{r boxplot crisp and vague, fig.width=3, fig.height=3}
dat %>% 
  gather(key=rt_metric, value=rt_value, rt_ms, rt_log, rt_reciprocal) %>%
  filter(rt_metric=="rt_log") %>%
  ggplot(aes(group=vag, y=rt_value)) +
  geom_boxplot(aes(x=vag, col=vag)) + 
  theme(aspect.ratio=1)
```

@@

```{r, "lmer 1 compare different rt metrics using the same model structure", warning=FALSE, cache=TRUE}
lmer1.ms  <- lmer(data=dat, rt_ms ~         vag + subit + quan + gap + side + (1|subject) + (1|item))
lmer1.log <- lmer(data=dat, rt_log ~        vag + subit + quan + gap + side + (1|subject) + (1|item))
lmer1.rcp <- lmer(data=dat, rt_reciprocal ~ vag + subit + quan + gap + side + (1|subject) + (1|item))

@@

dwplot(models, vline = geom_vline(xintercept = 0)) + facet_wrap(~model, scales="free", ncol=1)
```

```{r lmer on logrt, warning=FALSE, cache=TRUE}
lmer2.log <- lmer(data=dat, rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item))
dwplot(lmer2.log %>% tidy() %>% filter(group=="fixed")) + ggtitle("rt_log ~ vag * subit + quan + gap + side + (1+vag|subject) + (1+vag|item)")

lmer2.rcp <- lmer(data=dat, rt_reciprocal~subit*vag + (vag|subject) + (vag|item))

# lmer3 is closer to the original anova than lmer2
lmer3 <- tidy(lmer(data=dat, rt_reciprocal~vag*subit+quan+gap + (vag+subit|subject) + (vag|item)))
dwplot(lmer3 %>% filter(group=="fixed"), vline = geom_vline(xintercept = 0, colour = "grey50", linetype = 2)) + xlab("Coefficient")
```
